---
title: "Portfolio"
author: "Ouafaa Hmaddi"
date: "February 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

##Loading libraries 

```{r}
library(rio)
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(ggmap)
library(stringr)
library(waffle)
library(extrafont)
library(leaflet)
library(ggrepel)
library(gridExtra)
library(grid)
library(ggpubr)
```


##Importing data

```{r}

loans<- import("kiva_loans.csv", setclass = "tbl_df")
theme_id<- import("loan_theme_ids.csv", setclass = "tbl_df")
isoAlpha<- import("isoAlphacodes.csv", setclass = "tbl_df")

region<- import("kiva_mpi_region_locations.csv", setclass = "tbl_df")
theme_region<- import("loan_themes_by_region.csv", setclass = "tbl_df")

gini<- import("GINI.csv", setclass = "tbl_df")
colnames(gini) = gini[1, ]
gini = gini[-1,]

colnames(gini)[colnames(gini)=="Country Code"] <- "Alpha-3 code"
gini_iso2<- left_join(gini, isoAlpha, by="Alpha-3 code") 

colnames(gini_iso2)[colnames(gini_iso2)=="Alpha-2 code"] <- "country_code"
colnames(gini_iso2)[colnames(gini_iso2)=="2014"] <- "gini"
#theme_id %>% 
#    count(id) %>%
#    filter(n > 1)
loans_region <- left_join(loans, region, by='country')
```

##Joining GINI data with Kiva loans data

```{r fig.height=8}
loans1<- left_join(loans, theme_id) 

#loans_gdp<- left_join(loans1, gdp_iso2, by="country_code")

loans_gini<- left_join(loans1, gini_iso2, by="country_code")

#fund_gdp<-aggregate(funded_amount ~ country_code, data=loans_gdp, FUN=sum)
#colnames(fund_gdp)[colnames(fund_gdp)=="funded_amount"] <- "total_funds"

#totfund_gdp<-left_join(fund_gdp, loans_gdp, by="country_code")

loans_gini1<-na.omit(loans_gini)


fund_gini<-aggregate(funded_amount ~ country_code, data=loans_gini1, FUN=sum)
colnames(fund_gini)[colnames(fund_gini)=="funded_amount"] <- "total_funds"
totfund_gini<-left_join(fund_gini, loans_gini1, by="country_code")


```


##Top 10 countries using Kiva loans

```{r}

#What are the top 10 countries using kiva loans (regardless of the amount of loan), we are interested in the frequence of use of Kiva loans
Top_10<- loans %>%
  group_by(country) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ungroup() %>% 
  mutate(country = reorder(country,Count)) %>%
  head(10) 
#What is the gender distribution among this countries. We will now group by country and gender but keep only the top 10 countries by using a left join to our Top_10 dataset 
Top_10_g <- loans %>%
  group_by(country, borrower_genders) %>%
  summarise(Count_g = n()) %>%
  arrange(desc(Count_g)) %>%
  ungroup()  

Top_10_full <- left_join(Top_10, Top_10_g)  %>% 
  mutate(pct = Count_g/Count)

Top_10_full<-Top_10_full %>% separate(borrower_genders,c('g1','g2','g3','g4','g5','g6','g7','g8','g9','g10','g11','g12','g13','g14','g15','g16','g17','g18','g19','g20','g21','g22','g23', 'g24','g25','g26','g27','g28','g29','g30','g31','g32','g33','g34','g35','g36','g37','g38','g39','g40','g41','g42','g43','g44','g45'), sep=",")

Top_10_full<- select(Top_10_full, -c(g2:g45))

Top_10_full_g<-Top_10_full %>%
  group_by(country,g1, Count)%>%
  summarize(sum(Count_g))%>%
  mutate(pct=round((`sum(Count_g)`/Count)*100))%>%
  filter(g1!="")
  
#map(a, ~sum(is.na(.))) This is just to check if I covered all genders listed in the borrowers gender column. I stopped at g45 becasue as I added g46 all the the observations were missing which means I covered all of them at g45

p1<-ggplot(Top_10_full_g, aes(x = fct_reorder(country, Count),y = `sum(Count_g)`, fill=g1)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  geom_text(data=Top_10_full_g[9,], aes(label=g1), hjust=0.5,color="yellow")+
  geom_text(data=Top_10_full_g[10,], aes(label=g1), hjust =1.3)+
  labs(title= "Top 10 countries borrowing from Kiva by gender",
       subtitle = "Gender of the 1st member of the team",
       x="", y="")+
  scale_fill_viridis_d()+
  coord_flip()+
  theme_minimal()

```

##Mapping the number of loans brorowed from Kiva

```{r}
leaflet(theme_region) %>% addTiles() %>%
  addCircles(lng = ~lon, lat = ~lat,radius = ~(number) ,
             color = ~c("blue")) 
  
```

##World regions 

```{r}
p3<-loans_region %>%
  group_by(world_region) %>%
  summarise(Count = n()/1000000) %>%
  arrange(desc(Count)) %>%
  ungroup() %>% 
  mutate(world_region = reorder(world_region,Count)) %>%
  na.omit()%>%
  ggplot(aes(world_region, Count))+
  geom_bar(stat='identity',colour="white", fill="grey80")+
  coord_flip()+
  labs(x="", y="Number of loans in millions",
       title="Number of loans borrowed from Kiva by \n world region")+
  theme_minimal()

```

## Boxplot distribution of funded amount (logged)

```{r}
top_l<-loans_gini1 %>% select(`Loan Theme Type`, funded_amount) %>% top_n(50,wt=funded_amount) 

#ggplot(loans, aes(term_in_months, color=borrower_genders))+
#  geom_bar()+
#  scale_y_log10()

p4<-ggplot(top_l, aes(x=fct_reorder(`Loan Theme Type`,funded_amount), y= funded_amount, col=`Loan Theme Type`)) + 
  geom_boxplot(show.legend = FALSE) + 
  theme_minimal() + 
  scale_color_viridis_d()+
  scale_y_log10()+
  coord_flip() + 
  labs(x="", y="", 
       title="Boxplot distribution of funded amount",
       subtitle="Grouped by Loan Theme Type (top 50)")
```

```{r}
p2<-loans %>% select(sector,loan_amount)%>%
  group_by(sector)%>%
  summarise(sum_ta = sum(loan_amount))%>%
  mutate(perct = sum_ta/sum(loans$loan_amount)*100)%>%
  ggplot(aes(x= reorder(sector, perct),y = perct))+
  geom_bar(stat="identity",fill = "steelblue")+
  coord_flip()+
  geom_label(aes(label = round(perct,2)), size = 3, y= 2.5, col = "darkgreen")+
  theme_minimal()+
  theme(axis.text = element_text(size = 9),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
  labs(x="Sectors",
       y="Percentage",
       title= "Loans disribution by sector")
```


#Visualization 1
## Kiva at a glance

```{r fig.height=8, fig.width=11}
ggarrange(p4, p3, p1, p2 ,
          ncol = 2, nrow = 2)

```


##The use of the funded amount 

```{r }
kiva_words <- loans %>%
  unnest_tokens(word, use, token = "words")

kiva_words <- kiva_words %>%
  anti_join(stop_words)

kv_counts <- kiva_words %>%
  count(word, sort = TRUE)

kv_filter <- kv_counts %>%
  filter(n > 16000)

kv_filter_angle <- kv_filter %>%
  mutate(angle = 90 * sample(c(0, 1), n(), 
                             replace = TRUE, 
                             prob = c(50, 50)))
set.seed(12)

p5 <- ggplot(kv_filter_angle, aes(label = word, size = n, color = n, angle = angle)) +
  geom_text_wordcloud_area(rm_outside = TRUE) +
  scale_size_area(max_size = 25) +
  theme_minimal() +
  scale_color_distiller(palette = "Spectral")
```


###I was hoping for the word invest to be on the top but it does not even belong to the list. 

##How people tweet about the project

```{r }
kiva_tag <- loans %>%
  unnest_tokens(word, tags, token = "words")

kiva_tag <- kiva_tag %>%
  anti_join(stop_words) %>%
  filter(word !="user_favorite")

kvtag_counts <- kiva_tag %>%
  count(word, sort = TRUE)

kvtag_filter <- kvtag_counts %>%
  filter(n > 100)

kvtag_filter_angle <- kvtag_filter %>%
  mutate(angle = 90 * sample(c(0, 1), n(), 
                             replace = TRUE, 
                             prob = c(50, 50)))
set.seed(12)

p6 <- ggplot(kvtag_filter_angle, aes(label = word, size = n, color = n, angle = angle)) +
  geom_text_wordcloud_area(rm_outside = TRUE) +
  scale_size_area(max_size = 25) +
  theme_minimal() +
  scale_color_distiller(palette = "Spectral")

```

#Visualization 2
```{r fig.width=9}
ggarrange(p5, p6 , 
          ncol = 2, nrow = 1)
```

#Visualization 3
```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}

loans_gini11 <- left_join(loans_gini1, loans_region, by= "id" )
ggplot(loans_gini11, aes(funded_amount.x, gini ))+
  geom_point()+
  scale_x_log10()+
  theme_minimal()+
  labs(x="Funded Amount",
       y="GINI",
       title="")+
  facet_wrap(~world_region)


```


